The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-04-24 analysis/paper/paper.qmd
Update code chunk labels and fix references

```{r}
#| label: setup
#| echo: false
#| warning: false

@@

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache: true

@@

```{r}
#| label: clean-text
#| echo: false

@@

```{r}
#| label: fig-map-theses
#| warning: false 
#| echo: false
#| fig-cap: "Location of EMU theses included in the analysis"

@@

Figure @fig-map-theses shows the geographic spread of the theses included in the analysis.

@@

[@silge2017a] [@hvitfeldt2021a]

@@

```{r}
#| label: stop-words

@@

```{r}
#| label: stemming

>>>>

```{r setup}
#| echo: false
#| warning: false

@@

```{r extract-pdf-text}
#| echo: false
#| cache: true

@@

```{r clean-text}
#| echo: false

@@

```{r fig-map-theses}
#| warning: false 
#| echo: false
#| fig-cap: "Location of EMU theses included in the analysis"

@@

@fig-map-theses shows the geographic spread of the theses included in the analysis.

@@

@@

```{r stop-words}

@@

```{r stemming}
